---
title: "New Onboarding Flow after KYC completion"
author: "Dani Mermelstein"
date: "2020-12-04"
region: "US"
link: 
tags: "ab test, kyc, onboarding, acquire"
summary: "An AB test inserting a new screen post-KYC completion with onboarding instructions did not lead to improvements in core KPIs for the treatment group, possibly due to a lack of localization for the US"
output: 
  html_document:
    toc: TRUE
    theme: cosmo
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(data.table)
library(scales)
library(kableExtra)
library(tidyverse)
library(bayesAB)
library(ggplot2)

# load the data
load(paste0("data/onboarding.RData"))

# set outcomes
bayes <- onboarding
bayes$card_outcome <- 0
bayes[!is.na(bayes$card_first_activated)]$card_outcome <- 1
bayes$mau_outcome <- 0
bayes[!is.na(bayes$first_time_mau_tstamp)]$mau_outcome <- 1
bayes$second_outcome <- 0
bayes[!is.na(bayes$second_deposit)]$second_outcome <- 1

```

Data last updated on `r Sys.Date()`

# Assignments

```{r, echo=FALSE, message=FALSE}

ggplot(onboarding, aes(x=as.Date(assignment_date), fill=variant)) +
  geom_bar(stat="bin") +
  labs(title="Users Assigned per Day",
       x ="Date", 
       y = "Users")

```

# Analysis Output {.tabset .tabset-fade .tabset-pills}

## Card Activation {.tabset .tabset-fade}

```{r, echo=FALSE, message=FALSE}

AB1 <- bayesTest(bayes[variant=='treatment',]$card_outcome, bayes[variant=='control',]$card_outcome, priors = c('alpha' = 1, 'beta' = 1), n_samples = 1e5, distribution = 'bernoulli')

# aggregated stats
kable(data.frame("Variants"=c("control","treatment"),
           "Users"=c(length(bayes[variant=='control',]$card_outcome), length(bayes[variant=='treatment',]$card_outcome)),
           "Outcomes"=c(sum(bayes[variant=='control',]$card_outcome), sum(bayes[variant=='treatment',]$card_outcome)),
           "Rate"=c(sum(bayes[variant=='control',]$card_outcome)/length(bayes[variant=='control',]$card_outcome), sum(bayes[variant=='treatment',]$card_outcome)/length(bayes[variant=='treatment',]$card_outcome)))) %>%
  kable_styling(full_width = F)

# generate plots
images <- plot(AB1)
levels(images$posteriors$Probability$data$recipe) <- as.factor(c("treatment","control"))

# likelihood of improvement
loi <- summary(AB1)$probability
# confidence interval
ci <- summary(AB1)$interval$Probability

# determine whether the results are final or if test needs to run longer
print(ifelse((loi$Probability < 0.1 | loi$Probability > 0.9)&(0 < ci[[1]] | 0 > ci[[2]]), 'Test Complete', 'Keep Test Running'))

```

**90% confidence interval:**
```{r, echo=FALSE, message=FALSE}
print(ci)
```

**Estimated lift:**
```{r, echo=FALSE, message=FALSE}
print(percent(mean(c(ci))))
```

### Outcome Distribution
```{r, echo=FALSE, message=FALSE}
images$posteriors$Probability + ggtitle("Outcome Distribution")
```

### Likelihood of Improvement
```{r, echo=FALSE, message=FALSE}
images$samples$Probability + ggtitle("Likelihood of Improvement")

```

## Deposits {.tabset .tabset-fade}

### FT_MAU {.tabset .tabset-fade .tabset-pills}

```{r, echo=FALSE, message=FALSE}

AB1 <- bayesTest(bayes[variant=='treatment',]$mau_outcome, bayes[variant=='control',]$mau_outcome, priors = c('alpha' = 1, 'beta' = 1), n_samples = 1e5, distribution = 'bernoulli')

# generate plots
images <- plot(AB1)
levels(images$posteriors$Probability$data$recipe) <- as.factor(c("treatment","control"))

# likelihood of improvement
loi <- summary(AB1)$probability
# confidence interval
ci <- summary(AB1)$interval$Probability

# determine whether the results are final or if test needs to run longer
print(ifelse((loi$Probability < 0.1 | loi$Probability > 0.9)&(0 < ci[[1]] | 0 > ci[[2]]), 'Test Complete', 'Keep Test Running'))

# aggregated stats
kable(data.frame("Variants"=c("control","treatment"),
           "Users"=c(length(bayes[variant=='control',]$mau_outcome), length(bayes[variant=='treatment',]$mau_outcome)),
           "Outcomes"=c(sum(bayes[variant=='control',]$mau_outcome), sum(bayes[variant=='treatment',]$mau_outcome)),
           "Rate"=c(sum(bayes[variant=='control',]$mau_outcome)/length(bayes[variant=='control',]$mau_outcome), sum(bayes[variant=='treatment',]$mau_outcome)/length(bayes[variant=='treatment',]$mau_outcome)))) %>%
  kable_styling(full_width = F)

```

**90% confidence interval:**
```{r, echo=FALSE, message=FALSE}
print(ci)
```

**Estimated lift:**
```{r, echo=FALSE, message=FALSE}
print(percent(mean(c(ci))))
```


#### Outcome Distribution
```{r, echo=FALSE, message=FALSE}
images$posteriors$Probability + ggtitle("Outcome Distribution")
```

#### Likelihood of Improvement
```{r, echo=FALSE, message=FALSE}
images$samples$Probability + ggtitle("Likelihood of Improvement")

```

### FT_MAU Amount {.tabset .tabset-fade}


```{r, echo=FALSE, message=FALSE}
remove_outliers <- function(x, na.rm = TRUE, ...) {
  qnt <- quantile(x, probs=c(0, .98), na.rm = na.rm, ...)
  H <- 1.5 * IQR(x, na.rm = na.rm)
  y <- x
  y[x < (qnt[1] - H)] <- 0
  y[x > (qnt[2] + H)] <- 0
  y
}

control <- remove_outliers(as.integer(bayes[which(variant=='control' & !is.na(ft_funding_amount)),]$ft_funding_amount))
treatment <- remove_outliers(as.integer(bayes[which(variant=='treatment' & !is.na(ft_funding_amount)),]$ft_funding_amount))

amount_res <- wilcox.test(control, treatment, alternative=c("two.sided"), conf.level=.9, correct=TRUE, paired = FALSE)

print(ifelse(amount_res$p.value < 0.05, 'Results are significant', 'No difference between variants'))
```

Average deposit amounts:

 - Control: `r dollar(mean(control))`
 - Treatment: `r dollar(mean(treatment))`

Median deposit amounts:

 - Control: `r dollar(median(control))`
 - Treatment: `r dollar(median(treatment))`
 
```{r, echo=FALSE, message=FALSE}

ggplot(bayes, aes(x=ft_funding_amount, fill=variant)) +
  geom_density(alpha=.65) +
  xlim(0, 500)


```

### Second Deposit {.tabset .tabset-fade .tabset-pills}

```{r, echo=FALSE, message=FALSE}

AB1 <- bayesTest(bayes[variant=='treatment',]$second_outcome, bayes[variant=='control',]$second_outcome, priors = c('alpha' = 1, 'beta' = 1), n_samples = 1e5, distribution = 'bernoulli')

# generate plots
images <- plot(AB1)
levels(images$posteriors$Probability$data$recipe) <- as.factor(c("treatment","control"))

# likelihood of improvement
loi <- summary(AB1)$probability
# confidence interval
ci <- summary(AB1)$interval$Probability

# determine whether the results are final or if test needs to run longer
print(ifelse((loi$Probability < 0.1 | loi$Probability > 0.9)&(0 < ci[[1]] | 0 > ci[[2]]), 'Test Complete', 'Keep Test Running'))

# aggregated stats
kable(data.frame("Variants"=c("control","treatment"),
           "Users"=c(length(bayes[variant=='control',]$second_outcome), length(bayes[variant=='treatment',]$second_outcome)),
           "Outcomes"=c(sum(bayes[variant=='control',]$second_outcome), sum(bayes[variant=='treatment',]$second_outcome)),
           "Rate"=c(sum(bayes[variant=='control',]$second_outcome)/length(bayes[variant=='control',]$second_outcome), sum(bayes[variant=='treatment',]$second_outcome)/length(bayes[variant=='treatment',]$second_outcome)))) %>%
  kable_styling(full_width = F)

```

**90% confidence interval:**
```{r, echo=FALSE, message=FALSE}
print(ci)
```

**Estimated lift:**
```{r, echo=FALSE, message=FALSE}
print(percent(mean(c(ci))))
```

#### Outcome Distribution
```{r, echo=FALSE, message=FALSE}
images$posteriors$Probability + ggtitle("Outcome Distribution")
```

#### Likelihood of Improvement
```{r, echo=FALSE, message=FALSE}
images$samples$Probability + ggtitle("Likelihood of Improvement")

```

### Second Amount {.tabset .tabset-fade}


```{r, echo=FALSE, message=FALSE}

control <- remove_outliers(as.integer(bayes[which(variant=='control' & !is.na(second_deposit)),]$second_deposit_amount))
treatment <- remove_outliers(as.integer(bayes[which(variant=='treatment' & !is.na(second_deposit)),]$second_deposit_amount))

amount_res <- wilcox.test(control, treatment, alternative=c("two.sided"), conf.level=.9, correct=TRUE, paired = FALSE)

print(ifelse(amount_res$p.value < 0.05, 'Results are significant', 'No difference between variants'))
```

Average deposit amounts:

 - Control: `r dollar(mean(control))`
 - Treatment: `r dollar(mean(treatment))`

Median deposit amounts:

 - Control: `r dollar(median(control))`
 - Treatment: `r dollar(median(treatment))`
 
```{r, echo=FALSE, message=FALSE}

ggplot(bayes, aes(x=ft_funding_amount, fill=variant)) +
  geom_density(alpha=.65) +
  xlim(0, 500)


```
